---
title: "GWAS scrap"
author: "Sohini Guha"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load packages needed. Tidyverse include dplyer
require(tidyverse)
require(ggpubr)
require(ggplot2)
require(qqman)
knitr::opts_chunk$set(message = FALSE)
```


```{r Importing the data, echo=FALSE}
#Importing the psymA files

merged_psyma_ipd3.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_ipd3.change.tsv")
merged_psyma_latd.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_latd.change.tsv")
merged_psyma_hcl.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_hcl.change.tsv")
merged_psyma_dnf1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf1.change.tsv")
merged_psyma_dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf2.change.tsv")
merged_psyma_dnf3.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf3.change.tsv")
merged_psyma_dnf4.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf4.change.tsv")
merged_psyma_dnf6.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf6.change.tsv")
merged_psyma_dnf7.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf7.change.tsv")
merged_psyma_dnf1dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf5dnf2.change.tsv")
merged_psyma_dnf5dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_dnf5dnf2.change.tsv")
merged_psyma_nad1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_nad1change.tsv")
merged_psyma_rdn1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_rdn1.change.tsv")
merged_psyma_sunn1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_sunn1.change.tsv")
merged_psyma_sunn4.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_sunn4.change.tsv")
merged_psyma_A17<-read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psyma_subset_LD_ulmm_trait_A17.tsv")

#mypsyma_traits<-
#Importing the psymB files

merged_psymb_ipd3.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_ipd3.change.tsv")
merged_psymb_latd.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_latd.change.tsv")
merged_psymb_hcl.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_hcl.change.tsv")
merged_psymb_dnf1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf1.change.tsv")
merged_psymb_dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf2.change.tsv")
merged_psymb_dnf3.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf3.change.tsv")
merged_psymb_dnf4.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf4.change.tsv")
merged_psymb_dnf6.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf6.change.tsv")
merged_psymb_dnf7.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf7.change.tsv")
merged_psymb_dnf1dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf1dnf2.change.tsv")
merged_psymb_dnf5dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_dnf5dnf2.change.tsv")
merged_psymb_nad1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_nad1change.tsv")
merged_psymb_rdn1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_rdn1.change.tsv")
merged_psymb_sunn1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_sunn1.change.tsv")
merged_psymb_sunn4.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_sunn4.change.tsv")
merged_psymb_A17<-read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_psymb_subset_LD_ulmm_trait_A17.tsv")

#Importing the chromosome files
merged_chr_ipd3.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_ipd3.change.tsv")
merged_chr_latd.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_latd.change.tsv")
merged_chr_hcl.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_hcl.change.tsv")
merged_chr_dnf1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf1.change.tsv")
merged_chr_dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf2.change.tsv")
merged_chr_dnf3.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf3.change.tsv")
merged_chr_dnf4.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf4.change.tsv")
merged_chr_dnf6.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf6.change.tsv")
merged_chr_dnf7.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf7.change.tsv")
merged_chr_dnf1dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf1dnf2.change.tsv")
merged_chr_dnf5dnf2.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_dnf5dnf2.change.tsv")
merged_chr_nad1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_nad1change.tsv")
merged_chr_rdn1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_rdn1.change.tsv")
merged_chr_sunn1.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_sunn1.change.tsv")
merged_chr_sunn4.change <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_sunn4.change.tsv")
merged_chr_A17<-read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/gwas_results/annotation/merged_chr_subset_LD_ulmm_trait_A17.tsv")

#merging the chr,psyma,psymb for each gene

hcl_combined<-rbind(merged_chr_hcl.change,merged_psymb_hcl.change,merged_psyma_hcl.change)
dnf1_combined<-rbind(merged_chr_dnf1.change,merged_psyma_dnf1.change,merged_psymb_dnf1.change)
dnf2_combined<-rbind(merged_chr_dnf2.change,merged_psyma_dnf2.change,merged_psymb_dnf2.change)
dnf3_combined<-rbind(merged_chr_dnf3.change,merged_psyma_dnf3.change,merged_psymb_dnf3.change)
nad1_combined<-rbind(merged_chr_nad1.change,merged_psyma_nad1.change,merged_psymb_nad1.change)
ipd3_combined<-rbind(merged_chr_ipd3.change,merged_psyma_ipd3.change,merged_psymb_ipd3.change)
latd_combined<-rbind(merged_chr_latd.change,merged_psyma_latd.change,merged_psymb_latd.change)
dnf4_combined<-rbind(merged_chr_dnf4.change,merged_psyma_dnf4.change,merged_psymb_dnf4.change)
dnf7_combined<-rbind(merged_chr_dnf7.change,merged_psyma_dnf7.change,merged_psymb_dnf7.change)
dnf6_combined<-rbind(merged_chr_dnf6.change,merged_psyma_dnf6.change,merged_psymb_dnf6.change)
dnf1dnf2_combined<-rbind(merged_chr_dnf1dnf2.change,merged_psyma_dnf1dnf2.change,merged_psymb_dnf1dnf2.change)
dnf5dnf2_combined<-rbind(merged_chr_dnf5dnf2.change,merged_psyma_dnf5dnf2.change,merged_psymb_dnf5dnf2.change )
sunn1_combined<-rbind(merged_chr_sunn1.change,merged_psyma_sunn1.change,merged_psymb_sunn1.change)
rdn1_combined<-rbind(merged_chr_rdn1.change,merged_psyma_rdn1.change,merged_psymb_rdn1.change)
sunn4_combined<-rbind(merged_chr_sunn4.change,merged_psyma_sunn4.change,merged_psymb_sunn4.change)
A17_combined<-rbind(merged_chr_A17,merged_psyma_A17,merged_psymb_A17)


#writng the combined files
write.table(latd_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/latd_combined",sep = "\t",row.names = FALSE)
write.table(hcl_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/hcl_combined",sep = "\t",row.names = FALSE)
write.table(ipd3_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/ipd3_combined",sep = "\t",row.names = FALSE)
write.table(dnf1_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf1_combined",sep = "\t",row.names = FALSE)
write.table(dnf2_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf2_combined",sep = "\t",row.names = FALSE)
write.table(dnf3_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf3_combined",sep = "\t",row.names = FALSE)
write.table(dnf4_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf4_combined",sep = "\t",row.names = FALSE)
write.table(dnf6_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf6_combined",sep = "\t",row.names = FALSE)
write.table(dnf7_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf7_combined",sep = "\t",row.names = FALSE)
write.table(dnf1dnf2_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf1dnf2_combined",sep = "\t",row.names = FALSE)
write.table(dnf5dnf2_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/dnf5dnf2_combined",sep = "\t",row.names = FALSE)
write.table(nad1_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/nad1_combined",sep = "\t",row.names = FALSE)
write.table(rdn1_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/rdn1_combined",sep = "\t",row.names = FALSE)
write.table(sunn1_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/sunn1_combined",sep = "\t",row.names = FALSE)
write.table(sunn4_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/sunn4_combined",sep = "\t",row.names = FALSE)
write.table(A17_combined, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/A17_combined",sep = "\t",row.names = FALSE)
```

```{r creating the manhattan plot, echo=FALSE}
#GWAS_GENES<-c(dnf2_combined,dnf3_combined,nad1_combined,ipd3_combined,latd_combined,dnf7_combined,dnf6_combined,sunn4_combined)



hcl_combined$col2<-sapply(split_columns,'[',2)
ipd3_combined$col2<-sapply(split_columns,'[',2)
latd_combined$col2<-sapply(split_columns,'[',2)
nad1_combined$col2<-sapply(split_columns,'[',2)
dnf1_combined$col2<-sapply(split_columns,'[',2)
dnf2_combined$col2<-sapply(split_columns,'[',2)
dnf3_combined$col2<-sapply(split_columns,'[',2)
dnf4_combined$col2<-sapply(split_columns,'[',2)
dnf6_combined$col2<-sapply(split_columns,'[',2)
dnf7_combined$col2<-sapply(split_columns,'[',2)
dnf1dnf2_combined$col2<-sapply(split_columns,'[',2)
dnf5dnf2_combined$col2<-sapply(split_columns,'[',2)
rdn1_combined$col2<-sapply(split_columns,'[',2)
sunn1_combined$col2<-sapply(split_columns,'[',2)
sunn4_combined$col2<-sapply(split_columns,'[',2)









#early
hcl_combined$col2<-ifelse(hcl_combined$col2=="psymb",3,ifelse(hcl_combined$col2=="psyma",2,ifelse(hcl_combined$col2=="chr",1,hcl_combined$col2)))
ipd3_combined$col2<-ifelse(ipd3_combined$col2=="psymb",3,ifelse(ipd3_combined$col2=="psyma",2,ifelse(ipd3_combined$col2=="chr",1,ipd3_combined$col2)))
latd_combined$col2<-ifelse(latd_combined$col2=="psymb",3,ifelse(latd_combined$col2=="psyma",2,ifelse(latd_combined$col2=="chr",1,latd_combined$col2)))
#late
nad1_combined$col2<-ifelse(nad1_combined$col2=="psymb",3,ifelse(nad1_combined$col2=="psyma",2,ifelse(nad1_combined$col2=="chr",1,nad1_combined$col2)))
dnf1_combined$col2<-ifelse(dnf1_combined$col2=="psymb",3,ifelse(dnf1_combined$col2=="psyma",2,ifelse(dnf1_combined$col2=="chr",1,dnf1_combined$col2)))
dnf2_combined$col2<-ifelse(dnf2_combined$col2=="psymb",3,ifelse(dnf2_combined$col2=="psyma",2,ifelse(dnf2_combined$col2=="chr",1,dnf2_combined$col2)))
dnf3_combined$col2<-ifelse(dnf3_combined$col2=="psymb",3,ifelse(dnf3_combined$col2=="psyma",2,ifelse(dnf3_combined$col2=="chr",1,dnf3_combined$col2)))
dnf4_combined$col2<-ifelse(dnf4_combined$col2=="psymb",3,ifelse(dnf4_combined$col2=="psyma",2,ifelse(dnf4_combined$col2=="chr",1,dnf4_combined$col2)))
dnf6_combined$col2<-ifelse(dnf6_combined$col2=="psymb",3,ifelse(dnf6_combined$col2=="psyma",2,ifelse(dnf6_combined$col2=="chr",1,dnf6_combined$col2)))
dnf7_combined$col2<-ifelse(dnf7_combined$col2=="psymb",3,ifelse(dnf7_combined$col2=="psyma",2,ifelse(dnf7_combined$col2=="chr",1,dnf7_combined$col2)))
dnf1dnf2_combined$col2<-ifelse(dnf1dnf2_combined$col2=="psymb",3,ifelse(dnf1dnf2_combined$col2=="psyma",2,ifelse(dnf1dnf2_combined$col2=="chr",1,dnf1dnf2_combined$col2)))
dnf5dnf2_combined$col2<-ifelse(dnf5dnf2_combined$col2=="psymb",3,ifelse(dnf5dnf2_combined$col2=="psyma",2,ifelse(dnf5dnf2_combined$col2=="chr",1,dnf5dnf2_combined$col2)))
#AON
rdn1_combined$col2<-ifelse(rdn1_combined$col2=="psymb",3,ifelse(rdn1_combined$col2=="psyma",2,ifelse(rdn1_combined$col2=="chr",1,rdn1_combined$col2)))
sunn1_combined$col2<-ifelse(sunn1_combined$col2=="psymb",3,ifelse(sunn1_combined$col2=="psyma",2,ifelse(sunn1_combined$col2=="chr",1,sunn1_combined$col2)))
sunn4_combined$col2<-ifelse(sunn4_combined$col2=="psymb",3,ifelse(sunn4_combined$col2=="psyma",2,ifelse(sunn4_combined$col2=="chr",1,sunn4_combined$col2)))




hcl_combined$col2<-as.numeric(hcl_combined$col2)
ipd3_combined$col2<-as.numeric(ipd3_combined$col2)
latd_combined$col2<-as.numeric(latd_combined$col2)
nad1_combined$col2<-as.numeric(nad1_combined$col2)
dnf1_combined$col2<-as.numeric(dnf1_combined$col2)
dnf2_combined$col2<-as.numeric(dnf2_combined$col2)
dnf3_combined$col2<-as.numeric(dnf3_combined$col2)
dnf4_combined$col2<-as.numeric(dnf4_combined$col2)
dnf6_combined$col2<-as.numeric(dnf6_combined$col2)
dnf7_combined$col2<-as.numeric(dnf7_combined$col2)
dnf1dnf2_combined$col2<-as.numeric(dnf1dnf2_combined$col2)
dnf5dnf2_combined$col2<-as.numeric(dnf5dnf2_combined$col2)
rdn1_combined$col2<-as.numeric(rdn1_combined$col2)
sunn1_combined$col2<-as.numeric(sunn1_combined$col2)
sunn4_combined$col2<-as.numeric(sunn4_combined$col2)


manhattan(hcl_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_hcl$ldg)+title("hcl_combined change")
manhattan(ipd3_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_ipd3$ldg)+title("ipd3_combined change")
manhattan(latd_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_latd$ldg)+title("latd_combined change")

manhattan(nad1_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_nad1$ldg)+title("nad1_combined change")
manhattan(dnf1_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf1$ldg)+title("dnf1_combined change")
manhattan(dnf2_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf2$ldg)+title("dnf2_combined change")
manhattan(dnf3_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf3$ldg)+title("dnf3_combined change")
manhattan(dnf4_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf4$ldg)+title("dnf4_combined change")
manhattan(dnf6_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf6$ldg)+title("dnf6_combined change")
manhattan(dnf7_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf7$ldg)+title("dnf7_combined change")
manhattan(dnf1dnf2_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf1dnf2$ldg)+title("dnf1dnf2_combined change")
manhattan(dnf5dnf2_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_dnf5dnf2$ldg)+title("dnf5dnf2_combined change")

manhattan(sunn1_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_sunn1$ldg)+title("sunn1_combined change")
manhattan(sunn4_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_sunn4$ldg)+title("sunn4_combined change")
manhattan(rdn1_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",suggestiveline = F, genomewideline=F, highlight=top10_rdn1$ldg)+title("rdn1_combined change")









#plotting the beta ranks
# Identify the indices of the top 5 beta values
#top_indices <- order(latd_combined$beta, decreasing = TRUE)[1:5]
# Define custom labels for the x-axis (chromosomes)
#chromosome_labels <- c("1"="Chr","2"="psymA","3"="psymB")
#plot the manhattan
#manhattan(latd_combined,chr="col2",bp="ps",snp="ld_snps",p="p_lrt",snp_labels = chromosome_labels)+title("latd_combined change")

#labelling the hghest beta value 
#text(latd_combined$col2[highest_indices], latd_combined$beta[highest_indices], labels = format(latd_combined$rs[highest_indices], latd_combined$p_wald[highest_indices], digits = 2), pos = 4, col = "red")+title("Manhattan Plot with Annotated Highest Beta Values")

```

```{r top 10 candidates in each replicon, echo=FALSE}

#select the rows with pr >=1 and <=10 in the chromosome (can we write a function here????)

top10_chr_dnf1 <- subset(merged_chr_dnf1.change, pr >= 1 & pr <= 10)
top10_chr_dnf2 <- subset(merged_chr_dnf2.change, pr >= 1 & pr <= 10)
top10_chr_dnf3 <- subset(merged_chr_dnf3.change, pr >= 1 & pr <= 10)
top10_chr_dnf4 <- subset(merged_chr_dnf4.change, pr >= 1 & pr <= 10)
top10_chr_dnf6 <- subset(merged_chr_dnf6.change, pr >= 1 & pr <= 10)
top10_chr_dnf7<- subset(merged_chr_dnf7.change, pr >= 1 & pr <= 10)
top10_chr_dnf1dnf2 <- subset(merged_chr_dnf1dnf2.change, pr >= 1 & pr <= 10)
top10_chr_dnf5dnf2 <- subset(merged_chr_dnf5dnf2.change, pr >= 1 & pr <= 10)
top10_chr_nad1 <- subset(merged_chr_nad1.change, pr >= 1 & pr <= 10)
top10_chr_hcl <- subset(merged_chr_hcl.change, pr >= 1 & pr <= 10)
top10_chr_latd <- subset(merged_chr_latd.change, pr >= 1 & pr <= 10)
top10_chr_ipd3 <- subset(merged_chr_ipd3.change, pr >= 1 & pr <= 10)
top10_chr_rdn1 <- subset(merged_chr_rdn1.change, pr >= 1 & pr <= 10)
top10_chr_sunn1 <- subset(merged_chr_sunn1.change, pr >= 1 & pr <= 10)
top10_chr_sunn4 <- subset(merged_chr_sunn4.change, pr >= 1 & pr <= 10)
top10_chr_A17<-subset(merged_chr_A17,pr>=1 & pr<=10)
#select the rows with pr >=1 and <=10 in the psymA
top10_psyma_dnf1 <- subset(merged_psyma_dnf1.change, pr >= 1 & pr <= 10)
top10_psyma_dnf2 <- subset(merged_psyma_dnf2.change, pr >= 1 & pr <= 10)
top10_psyma_dnf3 <- subset(merged_psyma_dnf3.change, pr >= 1 & pr <= 10)
top10_psyma_dnf4 <- subset(merged_psyma_dnf4.change, pr >= 1 & pr <= 10)
top10_psyma_dnf6 <- subset(merged_psyma_dnf6.change, pr >= 1 & pr <= 10)
top10_psyma_dnf7<- subset(merged_psyma_dnf7.change, pr >= 1 & pr <= 10)
top10_psyma_dnf1dnf2 <- subset(merged_psyma_dnf1dnf2.change, pr >= 1 & pr <= 10)
top10_psyma_dnf5dnf2 <- subset(merged_psyma_dnf5dnf2.change, pr >= 1 & pr <= 10)
top10_psyma_nad1 <- subset(merged_psyma_nad1.change, pr >= 1 & pr <= 10)
top10_psyma_hcl <- subset(merged_psyma_hcl.change, pr >= 1 & pr <= 10)
top10_psyma_latd <- subset(merged_psyma_latd.change, pr >= 1 & pr <= 10)
top10_psyma_ipd3 <- subset(merged_psyma_ipd3.change, pr >= 1 & pr <= 10)
top10_psyma_rdn1 <- subset(merged_psyma_rdn1.change, pr >= 1 & pr <= 10)
top10_psyma_sunn1 <- subset(merged_psyma_sunn1.change, pr >= 1 & pr <= 10)
top10_psyma_sunn4 <- subset(merged_psyma_sunn4.change, pr >= 1 & pr <= 10)
top10_psyma_A17<-subset(merged_psyma_A17,pr>=1 & pr<=10)
#select the rows with pr >=1 and <=10 in the psymB
top10_psymb_dnf1 <- subset(merged_psymb_dnf1.change, pr >= 1 & pr <= 10)
top10_psymb_dnf2 <- subset(merged_psymb_dnf2.change, pr >= 1 & pr <= 10)
top10_psymb_dnf3 <- subset(merged_psymb_dnf3.change, pr >= 1 & pr <= 10)
top10_psymb_dnf4 <- subset(merged_psymb_dnf4.change, pr >= 1 & pr <= 10)
top10_psymb_dnf6 <- subset(merged_psymb_dnf6.change, pr >= 1 & pr <= 10)
top10_psymb_dnf7<- subset(merged_psymb_dnf7.change, pr >= 1 & pr <= 10)
top10_psymb_dnf1dnf2 <- subset(merged_psymb_dnf1dnf2.change, pr >= 1 & pr <= 10)
top10_psymb_dnf5dnf2 <- subset(merged_psymb_dnf5dnf2.change, pr >= 1 & pr <= 10)
top10_psymb_nad1 <- subset(merged_psymb_nad1.change, pr >= 1 & pr <= 10)
top10_psymb_hcl <- subset(merged_psymb_hcl.change, pr >= 1 & pr <= 10)
top10_psymb_latd <- subset(merged_psymb_latd.change, pr >= 1 & pr <= 10)
top10_psymb_ipd3 <- subset(merged_psymb_ipd3.change, pr >= 1 & pr <= 10)
top10_psymb_rdn1 <- subset(merged_psymb_rdn1.change, pr >= 1 & pr <= 10)
top10_psymb_sunn1 <- subset(merged_psymb_sunn1.change, pr >= 1 & pr <= 10)
top10_psymb_sunn4 <- subset(merged_psymb_sunn4.change, pr >= 1 & pr <= 10)
top10_psymb_A17<-subset(merged_psymb_A17,pr>=1 & pr<=10)

#writng the chromosomal top candidates
write.table(top10_chr_dnf1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf6, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf6.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf7, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf7.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf1dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf1dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf5dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf5dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_nad1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_nad1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_rdn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_rdn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_sunn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_sunn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_sunn4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_sunn4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_hcl, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_hcl.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_ipd3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_ipd3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_latd, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_latd.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_A17, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_A17.tsv",sep = "\t",row.names = FALSE)
#writng the psyma top candidates
write.table(top10_psyma_dnf1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf6, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf6.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf7, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf7.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf1dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf1dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf5dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf5dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_nad1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_nad1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_rdn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_rdn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_sunn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_sunn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_sunn4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_sunn4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_hcl, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_hcl.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_ipd3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_ipd3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_latd, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_latd.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_A17, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_A17.tsv",sep = "\t",row.names = FALSE)
#writng the psymb top candidates
write.table(top10_psymb_dnf1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf6, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf6.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf7, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf7.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf1dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf1dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf5dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf5dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_nad1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_nad1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_rdn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_rdn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_sunn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_sunn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_sunn4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_sunn4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_hcl, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_hcl.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_ipd3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_ipd3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_latd, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_latd.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_A17, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_A17.tsv",sep = "\t",row.names = FALSE)


#Combine the top 10 candidates per replicon

#chromosome
top10_chr <-rbind (top10_chr_dnf1,top10_chr_dnf1dnf2,top10_chr_dnf2,top10_chr_dnf3,top10_chr_dnf4,top10_chr_dnf4,top10_chr_dnf5dnf2,top10_chr_dnf6,top10_chr_dnf7,top10_chr_nad1,top10_chr_rdn1,top10_chr_sunn1,top10_chr_sunn4,top10_chr_hcl,top10_chr_latd,top10_chr_ipd3,top10_chr_A17)
#psyma
top10_psyma <-rbind (top10_psyma_dnf1,top10_psyma_dnf1dnf2,top10_psyma_dnf2,top10_psyma_dnf3,top10_psyma_dnf4,top10_psyma_dnf4,top10_psyma_dnf5dnf2,top10_psyma_dnf6,top10_psyma_dnf7,top10_psyma_nad1,top10_psyma_rdn1,top10_psyma_sunn1,top10_psyma_sunn4,top10_psyma_hcl,top10_psyma_latd,top10_psyma_ipd3,top10_psyma_A17)
#psymb
top10_psymb<-rbind (top10_psymb_dnf1,top10_psyma_dnf1dnf2,top10_psymb_dnf2,top10_psymb_dnf3,top10_psyma_dnf4,top10_psymb_dnf4,top10_psymb_dnf5dnf2,top10_psymb_dnf6,top10_psymb_dnf7,top10_psymb_nad1,top10_psymb_rdn1,top10_psymb_sunn1,top10_psymb_sunn4,top10_psymb_hcl,top10_psymb_latd,top10_psymb_ipd3,top10_psymb_A17)
#write the tables
write.table(top10_chr, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb.tsv",sep = "\t",row.names = FALSE)
#select the rows with prs>=0 in the replicons
prs_top10psyma<- subset(top10_psyma, prs >= 0)
prs_top10psymb<- subset(top10_psymb, prs >= 0)
prs_top10chr<- subset(top10_chr, prs >= 0)
#write the tables
write.table(prs_top10psyma, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/prs_top10chr.tsv",sep = "\t",row.names = FALSE)
write.table(prs_top10psyma, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/prs_top10psyma.tsv",sep = "\t",row.names = FALSE)
write.table(prs_top10psyma, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/prs_top10psymb.tsv",sep = "\t",row.names = FALSE)

```

```{r DONT RUN, echo=FALSE}

#writng the chromosomal top candidates
write.table(top10_chr_dnf1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf6, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf6.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf7, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf7.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf1dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf1dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_dnf5dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_dnf5dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_nad1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_nad1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_rdn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_rdn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_sunn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_sunn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_sunn4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_sunn4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_hcl, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_hcl.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_ipd3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_ipd3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_latd, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_latd.tsv",sep = "\t",row.names = FALSE)
write.table(top10_chr_A17, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_chr_A17.tsv",sep = "\t",row.names = FALSE)

#writng the psyma top candidates
write.table(top10_psyma_dnf1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf6, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf6.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf7, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf7.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf1dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf1dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_dnf5dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_dnf5dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_nad1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_nad1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_rdn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_rdn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_sunn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_sunn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_sunn4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_sunn4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_hcl, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_hcl.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_ipd3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_ipd3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_latd, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_latd.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psyma_A17, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psyma_A17.tsv",sep = "\t",row.names = FALSE)

#writng the psymb top candidates
write.table(top10_psymb_dnf1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf6, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf6.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf7, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf7.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf1dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf1dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_dnf5dnf2, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_dnf5dnf2.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_nad1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_nad1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_rdn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_rdn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_sunn1, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_sunn1.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_sunn4, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_sunn4.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_hcl, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_hcl.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_ipd3, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_ipd3.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_latd, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_latd.tsv",sep = "\t",row.names = FALSE)
write.table(top10_psymb_A17, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/top10_psymb_A17.tsv",sep = "\t",row.names = FALSE)

#combine top 10 candidates per genotype
top10_dnf1_1<-rbind(top10_chr_dnf1,top10_psyma_dnf1,top10_psymb_dnf1)
#Crosslinked table
top10_dnf1<- data.frame(group=dnf1_combined[match(unique(top10_dnf1_1$ld_group),dnf1_combined$ld_group),]$ld_group,
                Location=dnf1_combined[match(unique(top10_dnf1_1$ld_group),dnf2_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf1_1$ld_group),A17_combined$ld_group),]$pr,
                         dnf3rank=dnf3_combined[match(unique(top10_dnf1_1$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf1_1$ld_group),dnf4_combined$ld_group),]$pr

top10_dnf1_MAF_BETA<-data.frame(beta=top10_dnf1_1[match(unique(top10_dnf1_1$ld_group),top10_dnf1_1$beta),]$beta,maf=top10_dnf1_1[match(unique(top10_dnf1_1$ld_group),top10_dnf1_1$af),]$af)
                              
#dnf1_crosslinked<-inner_join(top10_dnf1,top10_dnf1_MAF_BETA, by="group")                
                                
      
                      maf=as.numeric (dnf1_combined[match(unique(top10_dnf1_1$ld_group),dnf1_combined$af),]$af),beta=dnf1_combined[match(unique(top10_dnf1_1$ld_group),dnf1_combined$beta),]$beta,



subset_df <- data.frame(top10_dnf1_1, c("ld_group", "af", "beta"))


Betas<-Betas[WTvnpd2top$group,]
```

```{r Generating the crosslinked GWAS table, echo=FALSE}


#combine top 10 candidates per genotype
top10_hcl<-rbind(top10_chr_hcl,top10_psyma_hcl,top10_psymb_hcl)
top10_ipd3<-rbind(top10_chr_ipd3,top10_psyma_ipd3,top10_psymb_ipd3)
top10_latd<-rbind(top10_chr_latd,top10_psyma_latd,top10_psymb_latd)
top10_nad1<-rbind(top10_chr_nad1,top10_psyma_nad1,top10_psymb_nad1)
top10_dnf1<-rbind(top10_chr_dnf1,top10_psyma_dnf1,top10_psymb_dnf1)
top10_dnf2<-rbind(top10_chr_dnf2,top10_psyma_dnf2,top10_psymb_dnf2)
top10_dnf3<-rbind(top10_chr_dnf3,top10_psyma_dnf3,top10_psymb_dnf3)
top10_dnf4<-rbind(top10_chr_dnf4,top10_psyma_dnf4,top10_psymb_dnf4)
top10_dnf6<-rbind(top10_chr_dnf6,top10_psyma_dnf6,top10_psymb_dnf6)
top10_dnf7<-rbind(top10_chr_dnf7,top10_psyma_dnf7,top10_psymb_dnf7)
top10_dnf1dnf2<-rbind(top10_chr_dnf1dnf2,top10_psyma_dnf1dnf2,top10_psymb_dnf1dnf2)
top10_dnf5dnf2<-rbind(top10_chr_dnf5dnf2,top10_psyma_dnf5dnf2,top10_psymb_dnf5dnf2)
top10_rdn1<-rbind(top10_chr_rdn1,top10_psyma_dnf1,top10_psymb_rdn1)
top10_sunn1<-rbind(top10_chr_sunn1,top10_psyma_sunn1,top10_psymb_sunn1)
top10_sunn4<-rbind(top10_chr_sunn4,top10_psyma_sunn4,top10_psymb_sunn4)
#pull out the ranks of the LD groups across all the genotypes
#dnf1
dnf1<- data.frame(group=dnf1_combined[match(unique(top10_dnf1$ld_group),dnf1_combined$ld_group),]$ld_group,
                Location=dnf1_combined[match(unique(top10_dnf1$ld_group),dnf1_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf1$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf1$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf1$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf1$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf1$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf1$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf1$ld_group),dnf2_combined$ld_grodnf2up),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf1$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf1$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf1$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf1$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf1$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf1$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf1$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf1$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf1$ld_group),rdn1_combined$ld_group),]$pr)
 
#lisitng out incorrect ranks
#considering not merging
#pulling out the ranks of the chromosomal candidates 
#dnf1

#dnf1_chr_ranks<- data.frame(group=dnf1_combined[match(unique(top10_chr_dnf1$ld_group),dnf1_combined$ld_group),]$ld_group,
                #Location=dnf1_combined[match(unique(top10_chr_dnf1$ld_group),top10_chr_dnf1$ld_group),]$chr,
                 #         WTrank=A17_combined[match(unique(top10_chr_dnf1$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_chr_dnf1$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_chr_dnf1$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_chr_dnf1$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_chr_dnf1$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_chr_dnf1$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_chr_dnf1$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_chr_dnf1$ld_groupp),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_chr_dnf1$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_chr_dnf1$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_chr_dnf1$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_chr_dnf1$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_chr_dnf1$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_chr_dnf1$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_chr_dnf1$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_chr_dnf1$ld_group),rdn1_combined$ld_group),]$pr)
 









               
#dnf2
dnf2<- data.frame(group=dnf2_combined[match(unique(top10_dnf2$ld_group),dnf2_combined$ld_group),]$ld_group,
                Location=dnf2_combined[match(unique(top10_dnf2$ld_group),dnf2_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf2$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf2$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf2$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf2$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf2$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf2$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf2$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf2$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf2$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf2$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf2$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf2$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf2$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf2$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf2$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf2$ld_group),rdn1_combined$ld_group),]$pr)
                
#dnf3
dnf3<- data.frame(group=dnf3_combined[match(unique(top10_dnf3$ld_group),dnf3_combined$ld_group),]$ld_group,
                Location=dnf3_combined[match(unique(top10_dnf3$ld_group),dnf3_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf3$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf3$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf3$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf3$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf3$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf3$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf3$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf3$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf3$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf3$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf3$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf3$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf3$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf3$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf3$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf3$ld_group),rdn1_combined$ld_group),]$pr)
#dnf4
dnf4<- data.frame(group=dnf4_combined[match(unique(top10_dnf4$ld_group),dnf4_combined$ld_group),]$ld_group,
                Location=dnf4_combined[match(unique(top10_dnf4$ld_group),dnf4_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf4$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf4$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf4$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf4$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf4$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf4$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf4$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf4$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf4$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf4$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf4$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf4$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf4$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf4$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf4$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf4$ld_group),rdn1_combined$ld_group),]$pr)
#dnf6
dnf6<- data.frame(group=dnf6_combined[match(unique(top10_dnf6$ld_group),dnf6_combined$ld_group),]$ld_group,
                Location=dnf6_combined[match(unique(top10_dnf6$ld_group),dnf6_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf6$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf6$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf6$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf6$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf6$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf6$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf6$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf6$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf6$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf6$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf6$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf6$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf6$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf6$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf6$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf6$ld_group),rdn1_combined$ld_group),]$pr)
#dnf7
dnf7<-data.frame(group=dnf7_combined[match(unique(top10_dnf7$ld_group),dnf7_combined$ld_group),]$ld_group,
                Location=dnf7_combined[match(unique(top10_dnf7$ld_group),dnf7_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf7$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf7$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf7$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf7$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf7$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf7$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf7$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf7$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf7$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf7$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf7$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf7$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf7$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf7$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf7$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf7$ld_group),rdn1_combined$ld_group),]$pr)
#dnf1dnf2
dnf1dnf2<- data.frame(group=dnf1dnf2_combined[match(unique(top10_dnf1dnf2$ld_group),dnf1dnf2_combined$ld_group),]$ld_group,
                Location=dnf1dnf2_combined[match(unique(top10_dnf1dnf2$ld_group),dnf1dnf2_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf1dnf2$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf1dnf2$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf1dnf2$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf1dnf2$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf1dnf2$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf1dnf2$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf1dnf2$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf1dnf2$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf1dnf2$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf1dnf2$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf1dnf2$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf1dnf2$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf1dnf2$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf1dnf2$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf1dnf2$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf1dnf2$ld_group),rdn1_combined$ld_group),]$pr)
#dnf5dnf2
dnf5dnf2<- data.frame(group=dnf5dnf2_combined[match(unique(top10_dnf5dnf2$ld_group),dnf5dnf2_combined$ld_group),]$ld_group,
                Location=dnf5dnf2_combined[match(unique(top10_dnf5dnf2$ld_group),dnf5dnf2_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_dnf5dnf2$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_dnf5dnf2$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_dnf5dnf2$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_dnf5dnf2$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_dnf5dnf2$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_dnf5dnf2$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_dnf5dnf2$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_dnf5dnf2$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_dnf5dnf2$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_dnf5dnf2$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_dnf5dnf2$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_dnf5dnf2$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_dnf5dnf2$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_dnf5dnf2$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_dnf5dnf2$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_dnf5dnf2$ld_group),rdn1_combined$ld_group),]$pr)
#rdn1
rdn1<- data.frame(group=rdn1_combined[match(unique(top10_rdn1$ld_group),rdn1_combined$ld_group),]$ld_group,
                Location=rdn1_combined[match(unique(top10_rdn1$ld_group),rdn1_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_rdn1$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_rdn1$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_rdn1$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_rdn1$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_rdn1$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_rdn1$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_rdn1$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_rdn1$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_rdn1$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_rdn1$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_rdn1$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_rdn1$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_rdn1$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_rdn1$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_rdn1$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_rdn1$ld_group),rdn1_combined$ld_group),]$pr)
#sunn1
sunn1<- data.frame(group=sunn1_combined[match(unique(top10_sunn1$ld_group),sunn1_combined$ld_group),]$ld_group,
                Location=sunn1_combined[match(unique(top10_sunn1$ld_group),sunn1_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_sunn1$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_sunn1$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_sunn1$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_sunn1$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_sunn1$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_sunn1$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_sunn1$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_sunn1$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_sunn1$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_sunn1$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_sunn1$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_sunn1$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_sunn1$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_sunn1$ld_group),rdn1_combined$ld_group),]$pr)
#sunn4
sunn4<- data.frame(group=sunn4_combined[match(unique(top10_sunn4$ld_group),sunn4_combined$ld_group),]$ld_group,
                Location=sunn4_combined[match(unique(top10_sunn4$ld_group),sunn4_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_sunn4$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_sunn4$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_sunn4$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_sunn4$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_sunn4$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_sunn4$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_sunn4$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_sunn4$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_sunn4$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_sunn4$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_sunn4$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_sunn4$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_sunn4$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_sunn4$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_sunn4$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_sunn4$ld_group),rdn1_combined$ld_group),]$pr)
#nad1
nad1<- data.frame(group=nad1_combined[match(unique(top10_nad1$ld_group),nad1_combined$ld_group),]$ld_group,
                Location=nad1_combined[match(unique(top10_nad1$ld_group),nad1_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_nad1$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_nad1$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_nad1$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_nad1$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_nad1$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_nad1$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_nad1$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_nad1$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_nad1$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_nad1$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_nad1$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_nad1$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_nad1$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_nad1$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_nad1$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_nad1$ld_group),rdn1_combined$ld_group),]$pr)
#latd
latd<- data.frame(group=latd_combined[match(unique(top10_latd$ld_group),latd_combined$ld_group),]$ld_group,
                Location=latd_combined[match(unique(top10_latd$ld_group),latd_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_latd$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_latd$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_latd$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_latd$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_latd$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_latd$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_latd$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_latd$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_latd$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_latd$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_latd$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_latd$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_latd$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_latd$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_latd$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_latd$ld_group),rdn1_combined$ld_group),]$pr)
#hcl
hcl<- data.frame(group=hcl_combined[match(unique(top10_hcl$ld_group),hcl_combined$ld_group),]$ld_group,
                Location=hcl_combined[match(unique(top10_hcl$ld_group),hcl_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_hcl$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_hcl$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_hcl$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_hcl$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_hcl$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_hcl$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_hcl$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_hcl$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_hcl$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_hcl$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_hcl$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_hcl$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_hcl$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_hcl$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_hcl$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_hcl$ld_group),rdn1_combined$ld_group),]$pr)
#ipd3
ipd3<- data.frame(group=ipd3_combined[match(unique(top10_ipd3$ld_group),ipd3_combined$ld_group),]$ld_group,
                Location=ipd3_combined[match(unique(top10_ipd3$ld_group),ipd3_combined$ld_group),]$chr,
                          WTrank=A17_combined[match(unique(top10_ipd3$ld_group),A17_combined$ld_group),]$pr,hclrank=hcl_combined[match(unique(top10_ipd3$ld_group),hcl_combined$ld_group),]$pr,ipd3rank=ipd3_combined[match(unique(top10_ipd3$ld_group),ipd3_combined$ld_group),]$pr,latdrank=latd_combined[match(unique(top10_ipd3$ld_group),latd_combined$ld_group),]$pr,nad1rank=nad1_combined[match(unique(top10_ipd3$ld_group),nad1_combined$ld_group),]$pr,dnf1rank=dnf1_combined[match(unique(top10_ipd3$ld_group),dnf1_combined$ld_group),]$pr,dnf2rank=dnf2_combined[match(unique(top10_ipd3$ld_group),dnf2_combined$ld_group),]$pr,dnf3rank=dnf3_combined[match(unique(top10_ipd3$ld_group),dnf3_combined$ld_group),]$pr,dnf4rank=dnf4_combined[match(unique(top10_ipd3$ld_group),dnf4_combined$ld_group),]$pr,dnf6rank=dnf6_combined[match(unique(top10_ipd3$ld_group),dnf6_combined$ld_group),]$pr,dnf7rank=dnf7_combined[match(unique(top10_ipd3$ld_group),dnf7_combined$ld_group),]$pr,dnf1dnf2rank=dnf1dnf2_combined[match(unique(top10_ipd3$ld_group),dnf1dnf2_combined$ld_group),]$pr,dnf5dnf2rank=dnf5dnf2_combined[match(unique(top10_ipd3$ld_group),dnf5dnf2_combined$ld_group),]$pr,sunn1rank=sunn1_combined[match(unique(top10_ipd3$ld_group),sunn1_combined$ld_group),]$pr,sunn4rank=sunn4_combined[match(unique(top10_ipd3$ld_group),sunn4_combined$ld_group),]$pr,rdn1rank=rdn1_combined[match(unique(top10_ipd3$ld_group),rdn1_combined$ld_group),]$pr)

#Merge

GWAS_crosslinked<-rbind(hcl,ipd3,latd,nad1,dnf1,dnf2,dnf3,dnf4,dnf6,dnf7,dnf1dnf2,dnf5dnf2,rdn1,sunn1,sunn4)
write.table<(GWAS_crosslinked, file="~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/NSFPGRP_HostMutants/Data/GWAS_SOHINI/top 10 candidates/crosslinked_GWAS.tsv",sep = "\t",row.names = FALSE))
```               
                         
                         
```  
```#{r Nucleotide diversity analysis, echo=FALSE}
pdf(file = "/Users/sohiniguha/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Sohini&Liana/GitHub/HostMutants2021_C86meliloti/figures/tajima.pdf",width = 6.78, height = 6.78)

summarized_rhizobia_data <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Burghardt Lab Shared Folder/Projects/TiffinLabSharedData/popgen/rhizobia/summarized_rhizobia_data.tsv")

#top5 in the small group
split_data <- strsplit(top5_candidates_prs.1$description, ":")
split_data <- sapply(split_data, function(top5_candidates_prs.1) top5_candidates_prs.1[1])
split_data
# Assuming split_data contains the locus tags you want to filter by
filtered_data <- summarized_rhizobia_data[summarized_rhizobia_data$ncbi_locus_tag %in% split_data, ]

# Extracting the tajD values from the filtered data
filtered_tajD_values <- filtered_data$tajD

# Set theme options
theme_set(theme_minimal(base_size = 12))

# Plotting the density and vertical lines
ggplot(summarized_rhizobia_data, aes(x = tajD)) +
     geom_density(fill = "skyblue", alpha = 0.6) +  # Adjust density plot appearance
    geom_vline(data = filtered_data, aes(xintercept = tajD, color = filtered_data$replicon), linetype = "dashed") +  # Add vertical lines with color mapping
    labs(title = "Tajima's D with top5 candidates and the pcut",x = "Tajima's D",
          y = "Density") +  # Adjust axis labels
    theme(plot.title = element_text(size = 16, face = "bold"),  # Adjust title appearance
          axis.text = element_text(size = 10),  # Adjust axis text size
           axis.title = element_text(size = 12, face = "bold"))+scale_color_manual(values = c("black", "firebrick", "forestgreen"))  # Customizing color palette


  


#changing the pcut and expanding beyond top5
get_top_candidates_subset_and_combine.1 <- function(data) {
  top_candidates_subset.1 <- subset(data, p_lrt <= 1e-5)
  return(top_candidates_subset.1)
}

# Use lapply to apply the function to each data frame
all_top_candidates_subsets.1 <- lapply(data_list, get_top_candidates_subset_and_combine.1)

# Combine all subsets into a single data frame
combined_data2 <- do.call(rbind, all_top_candidates_subsets.1)

Candidates_pcut<-combined_data2%>% separate(chr,c('Organism','Replicon'))


split_data <- strsplit(Candidates_pcut$description, ":")
split_data <- sapply(split_data, function(Candidates_pcut) Candidates_pcut[1])
split_data
# Assuming split_data contains the locus tags you want to filter by
filtered_data <- summarized_rhizobia_data[summarized_rhizobia_data$ncbi_locus_tag %in% split_data, ]

# Extracting the tajD values from the filtered data
filtered_tajD_values <- filtered_data$tajD

#myplot
#ggplot(summarized_rhizobia_data, aes(x = tajD)) +geom_density(alpha = 0.6) +geom_vline(data = data.frame(tajD = tajD_values), aes(xintercept = tajD), color = "red")
#prettier plot

# Set theme options
theme_set(theme_minimal(base_size = 12))

# Plotting the density and vertical lines
ggplot(summarized_rhizobia_data, aes(x = tajD)) +
     geom_density(fill = "skyblue", alpha = 0.6) +  # Adjust density plot appearance
    geom_vline(data = filtered_data, aes(xintercept = tajD, color = filtered_data$replicon), linetype = "dashed") +  # Add vertical lines with color mapping
    labs(title = "Tajima's D with pcut p_lrt <= 1e-5",x = "Tajima's D",
          y = "Density") +  # Adjust axis labels
    theme(plot.title = element_text(size = 16, face = "bold"),  # Adjust title appearance
          axis.text = element_text(size = 10),  # Adjust axis text size
           axis.title = element_text(size = 12, face = "bold"))+scale_color_manual(values = c("black", "firebrick", "forestgreen"))  # Customizing color palette


##prs

Candidates_prs<-Candidates_pcut%>% filter(!is.na(as.numeric(prs)))

split_data <- strsplit(Candidates_prs$description, ":")
split_data <- sapply(split_data, function(Candidates_prs) Candidates_prs[1])
split_data
# Assuming split_data contains the locus tags you want to filter by
filtered_data <- summarized_rhizobia_data[summarized_rhizobia_data$ncbi_locus_tag %in% split_data, ]

# Extracting the tajD values from the filtered data
filtered_tajD_values <- filtered_data$tajD
# Set theme options
theme_set(theme_minimal(base_size = 12))

# Plotting the density and vertical lines
ggplot(summarized_rhizobia_data, aes(x = tajD)) +
     geom_density(fill = "skyblue", alpha = 0.6) +  # Adjust density plot appearance
    geom_vline(data = filtered_data, aes(xintercept = tajD, color = filtered_data$replicon), linetype = "dashed") +  # Add vertical lines with color mapping
    labs(title = "Tajima's D with pcut and prs only",x = "Tajima's D",
          y = "Density") +  # Adjust axis labels
    theme(plot.title = element_text(size = 16, face = "bold"),  # Adjust title appearance
          axis.text = element_text(size = 10),  # Adjust axis text size
           axis.title = element_text(size = 12, face = "bold"))+scale_color_manual(values = c("black", "firebrick", "forestgreen"))  # Customizing color palette

#faceting by replicons
#original density plot 
ggplot(summarized_rhizobia_data, aes(x = tajD))+geom_density(fill = "skyblue", alpha = 0.6)+ facet_wrap(vars(replicon))+geom_vline(data = filtered_data, aes(xintercept = tajD, color = filtered_data$replicon), linetype = "dashed") +  # Add vertical lines with color mapping
    labs(title = "Tajima's D with prs and faceted",x = "Tajima's D",
         y = "Density") +  # Adjust axis labels
    theme(plot.title = element_text(size = 16, face = "bold"),  # Adjust title appearance
          axis.text = element_text(size = 10),  # Adjust axis text size
          axis.title = element_text(size = 12, face = "bold"))+scale_color_manual(values = c("black", "firebrick", "forestgreen"))  # Customizing color palette
#overlay of the 3 replicons
ggplot(summarized_rhizobia_data, aes(x=tajD,fill=replicon))+ geom_density(aes(group=replicon),alpha=0.5)+geom_vline(data = filtered_data, aes(xintercept = tajD, color = filtered_data$replicon), linetype = "dashed") +  # Add vertical lines with color mapping
    labs(title = "Tajima's D with prs and overlayed",x = "Tajima's D",
         y = "Density") +  # Adjust axis labels
    theme(plot.title = element_text(size = 16, face = "bold"),  # Adjust title appearance
          axis.text = element_text(size = 10),  # Adjust axis text size
          axis.title = element_text(size = 12, face = "bold"))+scale_color_manual(values = c("black", "firebrick", "forestgreen"))  # Customizing color palette

dev.off()
```





